Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-10 paper/paper.tex
edits
spell checking and minor change in abstract

\author{Jefferson Silva \and Igor Lima \and Breno Miranda\footnotemark
  \and Gustavo Pinto \and Marcelo d'Amorim}
%\authorrunning{Short form of author list} % if too long for running head

\institute{
* Corresponding author: Breno Miranda \and \email{bafm@cin.ufpe.br}\\ \\
Jefferson Silva \and \email{jefferson.alves.silva@icen.ufpa.br}\\
Igor Lima \and \email{isol2@cin.ufpe.br} \\
Gustavo Pinto \and \email{gpinto@ufpa.br} \\
Breno Miranda \and \email{bafm@cin.ufpe.br} \\
Marcelo d'Amorim \and \email{damorim@cin.ufpe.br} \\
\at Universidade Federal de Pernambuco, Recife, PE, Brazil}

@@

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suite exists for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests in that stuite fail
regularly in the most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

@@

\emph{Key Findings.}~We found that--1)~Differential testing and Test
Transplation are practical and effective techniques to find bugs on real,
complex, and widely used software systems, 2)~Even for problems with
fairly clear specifications, as in \javascript{}, there is likely (a
lot of) variation between different implementations, which brings instrinsic
challenges to developers that work on them.
Section~\ref{sec:lessons} expands and elaborates key
findings and lessons learned.

@@

\section{Mined JS Files}
\label{sec:seeds}
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines (ie., Duktape, JerryScript, JSI, and Tiny-js),
4) test files mined from issue trackers of
these engines, and 5) test files from other GitHub projects.

@@

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use the default
well-known assertions available in JS, which the other JS engines use.
Instead, it uses its own testing framework, WScript. In this case, we could
not easily reproduce the \chakra unit tests in the other engines since it would
raise a ReferenceError. Also, updating the other engines to use WScript would
require a non-trivial manual process.}

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
    shows the tests used for test transplantation (resp., cross-engine
    differential testing).\Gustavo{Terminar essa tabela}}  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    \chakra & \cite{chakra2018repo}\\
    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    \midrule
    GitHub Projects & - & 494,394 & - & - & - \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers

>>>>

\author{Igor Lima \and Jefferson Silva \and Breno Miranda\footnotemark
  \and Gustavo Pinto \and Marcelo d'Amorim}
%\authorrunning{Short form of author list} % if too long for running head

\institute{
* Corresponding author: Breno Miranda \and
\email{bafm@cin.ufpe.br}\\ \\
Igor Lima \and \email{isol2@cin.ufpe.br} \\
Jefferson Silva \and \email{jefferson.alves.silva@icen.ufpa.br}\\
Breno Miranda \and \email{bafm@cin.ufpe.br} \\
Gustavo Pinto \and \email{gpinto@ufpa.br} \\
Marcelo d'Amorim \and \email{damorim@cin.ufpe.br} \\
\at Universidade Federal de Pernambuco, Recife, PE, Brazil}

@@

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suite exists for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests in that suite fail
regularly in the most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

@@

\emph{Key Findings.}~We found that--1)~Differential testing and Test
Transplantation are practical and effective techniques to find bugs on real,
complex, and widely used software systems, 2)~Even for problems with
fairly clear specifications, as in \javascript{}, there is likely (a
lot of) variation between different implementations, which brings intrinsic
challenges to developers that work on them.
Section~\ref{sec:lessons} expands and elaborates key
findings and lessons learned.

@@

\section{Mined JS Files}
\label{sec:seeds}
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines (\ie{}, Duktape, JerryScript, JSI, and Tiny-js),
4) test files mined from issue trackers of
these engines, and 5) test files from other GitHub projects.

@@

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use the default
well-known assertions available in JS, which the other JS engines use.
Instead, it uses its own testing framework, WScript. In this case, we could
not easily reproduce the \chakra unit tests in the other engines since it would
raise a ReferenceError. Also, updating the other engines to use WScript would
require a non-trivial manual process. This is why \chakra is not showed
in Table~\ref{tab:test-suites}.}

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
    shows the tests used for test transplantation (resp., cross-engine
    differential testing).\Gustavo{Terminar essa tabela}}  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    \midrule
    GitHub Projects & - & 494,394 & - & - & - \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator de
%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno
% LocalWords:  d'Amorim Universidade Pernambuco
